Plotting the Single-Electron Solution to Schr\"{o}dinger's Equation with OpenCL

### 2010-05-05 paper/paper.tex
more clarity about a thing
Remove various things

\begin{equation}\label{psi}
\psi\left(n, l, m\right)=\psi_c
\left(\mathit{e}^{-r/na}\right)
\left(\frac{2r}{na}\right)^l
\left[L_{n-l-1}^{2l+1}
    \left(\frac{2r}{na}\right)\right]
Y_l^m\left(\theta,\phi\right),
\end{equation}

\begin{equation}\label{psiConstant}
\psi_c=\sqrt{\left(\frac{2}{na}\right)^3
    \frac{\left(n-l-1\right)!}{2n\left[\left(n+l\right)!\right]^3}}.
\end{equation}

@@

@@

The decision was made during the implementation phase to redefine the Bohr radius so that $a=1$; this was done in order to keep intermediate numbers within the range of single-precision floating point values, as OpenCL doesn't currently support native double-precision math on any of the GPUs available for benchmarking. Since we're only using this software to generate visualizations, this doesn't affect the output; it simply scales the distances away from the atomic level.

@@

>>>>

\begin{equation}\label{psi}
\psi\left(n, l, m\right)=\psi_c
\left(\mathit{e}^{-r/n}\right)
\left(\frac{2r}{n}\right)^l
\left[L_{n-l-1}^{2l+1}
    \left(\frac{2r}{n}\right)\right]
Y_l^m\left(\theta,\phi\right),
\end{equation}

\begin{equation}\label{psiConstant}
\psi_c=\sqrt{\left(\frac{2}{n}\right)^3
    \frac{\left(n-l-1\right)!}{2n\left[\left(n+l\right)!\right]^3}}.
\end{equation}

@@

\subsection{Overview}

@@

\subsection{Simplifications}

The decision was made during the implementation phase to redefine the Bohr radius so that $a=1$; this was done in order to keep intermediate numbers within the range of single-precision floating point values, as OpenCL doesn't currently support native double-precision math on any of the GPUs available for benchmarking. Since we're only using this software to generate visualizations, this doesn't affect the output; it simply scales the distances away from the atomic level. The equations above have $a=1$ already substituted in, for brevity.

To keep the implementation of this algorithm within the scope of this project, we also decided to use a fixed-camera orthogonal projection. This worked to significantly simplify the process of iteration over all of the samples, as with this restriction, the program simply has to iterate over all of the pixels in the image, evaluating $n$ points in the $z$ dimension for each pixel, without worrying about complex transformations between coordinate systems.

@@

As one can see in \ref{fig:runtimePlot}, both GPUs significantly outperform all of the CPUs
